2.3 Prob Model for PCR Positivity Estimation

### 2024-04-19 2_scripts/2.3 Prob Model for PCR pos.qmd
Update the codes for figure about Abb~Roch transformation

p03r<-tb_ro_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=assay, colour=assay)) +
  geom_point(aes(colour=assay)) +
  geom_line(aes(colour=assay))  +
  theme_bw() 
p03r
```

@@

p04
```

>>>>

p03r<-tb_ro_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=assay, colour=assay)) +
  geom_point(aes(colour=assay)) +
  geom_line(aes(colour=assay))  +
  theme_bw() 
p03r
```
#### 3.3.3 Plot both roche and abbott, raw/transformed in on figure
```{r}
# modify melted data

## raw and transformed
tb_ro_melt$raw[tb_ro_melt$assay=="prop.abbott"]<-"raw"
tb_ro_melt$raw[tb_ro_melt$assay=="prop.roche"]<-"transformed"

tb_abb_melt2<-tb_abb_melt %>%
  .[.$region=="Alberta",] %>%
  select(1,3,4)
tb_abb_melt2$raw[tb_abb_melt2$assay=="prop.roche"]<-"raw"
tb_abb_melt2$raw[tb_abb_melt2$assay=="prop.abbott"]<-"transformed"

## Alberta only
tb_alberta<-bind_rows(tb_ro_melt, tb_abb_melt2)

## add a data source indicator
table(tb_alberta$assay, tb_alberta$raw)
tb_alberta$data[tb_alberta$assay=="prop.abbott"
                & tb_alberta$raw=="raw"]<-"APL"
tb_alberta$data[tb_alberta$assay=="prop.roche"
                & tb_alberta$raw=="transformed"]<-"APL"
tb_alberta$data[tb_alberta$assay=="prop.abbott"
                & tb_alberta$raw=="transformed"]<-"CBS"
tb_alberta$data[tb_alberta$assay=="prop.roche"
                & tb_alberta$raw=="raw"]<-"CBS"
table(tb_alberta$data, tb_alberta$assay)
table(tb_alberta$data, tb_alberta$raw)
```

Alton's comments:
- solid/dash to indicate raw/transformed
- red/blue to indicate Abbott/Roche

```{r}
# making the plot, 
p03.3<-tb_alberta %>%
  ggplot(aes(x=samplemonth, y=prop, colour=data)) +
  geom_point(aes(colour=data, shape=raw)) +
  geom_line(aes(colour=data, linetype=raw))  +
  theme_bw() + 
  xlab("Time of Sample Collection") + 
  ylab("Sero-prevalence") 
p03.3
```

@@

p04
```
#### Add alternative COI
```{r}
## add two new COI, those two were transformed using the model lm01 and lm01r
df.temp<-as.data.frame(c(log(1.0)))
colnames(df.temp)<-c("log_roche_n")
COI_abbott_t<-predict(lm01, newdata = df.temp, "response")

df.temp<-as.data.frame(c(log(1.4)))
colnames(df.temp)<-c("log_abbott_n")
COI_roche_t<-predict(lm01r, newdata = df.temp, "response")

p04 +   
  geom_vline(xintercept = COI_roche_t, linewidth=1.0, linetype="dotted", col="orange") +
  geom_hline(yintercept = COI_abbott_t, linewidth=1.0, linetype="dotted", col="orange")

## Use model lm01 coeff to calculate the Roche COI
COI_roche_t2<-(log(1.4)-as.numeric(lm01$coefficients[1]))/as.numeric(lm01$coefficients[2])
COI_abbott_t2<-(log(1.0)-as.numeric(lm01r$coefficients[1]))/as.numeric(lm01r$coefficients[2])

p04<-p04 +   
  geom_vline(xintercept = COI_roche_t2, linewidth=1.0, linetype="dotted", col="darkgreen") +
  geom_hline(yintercept = COI_abbott_t2, linewidth=1.0, linetype="dotted", col="darkgreen")
```
